---
title: "Tweets"
author: "Mariateresa Russo"
date: "2024-05-06"
output:
  html_document: default
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

## French parties analyzed in this study

1)France Insoumise: France Insoumise is a left-wing political movement
founded in 2016 by Jean-Luc Mélenchon, a long-time French politician.
The movement opposes neoliberalism, globalization, and defends more
progressive policies such as higher taxes on the wealthy and the fight
against austerity. It defines itself as anticapitalist and promotes
greater participatory democracy. At the European level, France Insoumise
is affiliated with the European United Left/Nordic Green Left group in
the European Parliament. 2)Les Républicains: Les Républicains,
previously known as UMP (Union for a Popular Movement), are a
center-right party in France. The party was founded in 2002 by a broad
coalition of center-right and right-wing parties. Les Républicains
support conservative policies including free market principles, reducing
public spending, and a stricter immigration policy. At the European
level, Les Républicains are affiliated with the European People's Party
(EPP), a political group that includes many other European center-right
parties. 3)Les Verts: Les Verts, or Europe Écologie-Les Verts (EELV), is
an ecologist political party in France. It was founded in 1984 and is
the main ecologist party in the country. Les Verts focuses on
environmental protection, sustainability, and combating climate change.
The party supports policies such as renewable energy, reducing
greenhouse gas emissions, and promoting public transportation. At the
European level, Les Verts are part of the Greens/European Free Alliance
group in the European Parliament. 4)Parti Socialiste: The Socialist
Party is a center-left party in France. Founded in 1969, the party has
traditionally supported social democratic policies such as social
welfare, redistribution of resources, and increased economic regulation.
However, over the years, the Socialist Party has undergone various
ideological transformations. At the European level, the 5)Socialist
Party is affiliated with the Progressive Alliance of Socialists and
Democrats group in the European Parliament. Place Publique: Place
Publique is a progressive political movement founded in 2018 by Raphaël
Glucksmann, a French intellectual and journalist. The movement focuses
on defending democracy, human rights, the environment, and progressive
social policies. It was a significant player in the 2019 European
elections in France. At the European level, Place Publique is associated
with the Progressive Alliance of Socialists and Democrats group in the
European Parliament. 6)Rassemblement National: Rassemblement National,
previously known as the National Front, is a far-right political party
in France. Founded in 1972 by Jean-Marie Le Pen, the party is known for
its anti-immigration, eurosceptic, and nationalist positions. It opposes
globalization and supports policies of national sovereignty. At the
European level, Rassemblement National is associated with the Identity
and Democracy group in the European Parliament. 7)Reconquête: Reconquête
is a right-wing French political movement founded by Éric Zemmour, a
prominent journalist and writer. The movement opposes immigration and
promotes traditional conservative policies. Reconquête has gained
attention for its positions against multiculturalism and for the defense
of French identity. It is not associated with a specific group in the
European Parliament. 8)Renaissance: Renaissance is a progressive
political movement founded by French President Emmanuel Macron in view
of the 2019 European elections. The movement supports liberal,
pro-European, and reformist policies. It focuses on modernizing the
French economy, promoting European solidarity, and combating climate
change. At the European level, Renaissance is associated with the Renew
Europe group in the European Parliament.

## European parties

(GUE/NGL) - European United Left/Nordic Green Left (EPP) - European
People's Party Greens/EFA - Greens/European Free Alliance (S&D) -
Progressive Alliance of Socialists and Democrats (ID) - Identity and
Democracy (RE) - Renew Europe (ECR) - European Conservatives and
Reformists

```{r}
party <- c("France Insoumise", "Les Républicains", "Les Verts", "Parti Socialiste", "Place Publique", "Rassemblement National", "Reconquête", "Renaissance")
european_movement <- c("GUE_NGL", "EPP", "Verts_ALE", "S&D", "S&D", "ID", "ECR", "RE")
orientation <- c("Left", "Centre-Right", "Centre", "Centre-Left", "Centre-Left","Right", "Right","Centre")
leader <- c("Jean-Luc Mélenchon", "Éric Ciotti", "Marine Tondelier", "Olivier Faure", "Raphaël Glucksmann", "Marine Le Pen", "Éric Zemmour", "Emmanuel Macron")

#da cambiare+vedere se place publique e parti socialiste si sono uniti
candidate <-c("Manon Aubry", "François-Xavier Bellamy", "Marie Toussaint", "Raphaël Glucksmann ", "Raphaël Glucksmann","Jordan Barella", "Marion Maréchal ", "Valérie Hayer")

parties <- data.frame(Party = party, European_movement = european_movement, Orientation = orientation, Leader = leader, European_candidate = candidate)
print(parties)
```

## Start the analysis

```{r}
suppressWarnings({
library(readxl)
library(tm)
library(textstem)
library(dplyr)
library(ggplot2)
library(rlang)
library(tidymodels)

library(koRpus)
library(quanteda)
library(udpipe)
})
```

The dataset

```{r}
library(readxl)
df <- read_excel("C:/Users/maria/OneDrive/Documents/Mery/scuola/Social media analytics/Elezioni Francia Dati_grezzi.xlsx", sheet = 1)
```

rename the labels

```{r}
table(df$Profile)

df$Profile[df$Profile %in% 'FranceInsoumise'] <- 'France_Insoumise'
df$Profile[df$Profile %in%  'Parti Socialiste'] <- 'Parti_Socialiste'
df$Profile[df$Profile %in%  'les Républicains'] <- 'Les_Republicains'
df$Profile[df$Profile %in%  'EELV'] <- 'Les_Verts'
df$Profile[df$Profile %in%  'Place publique'] <- 'Place_Publique'
df$Profile[df$Profile %in%  'RECONQUÊTE'] <- 'Reconquete'
df$Profile[df$Profile %in%  'Rassemblement National'] <- 'Rassemblement_National'
df$Profile[df$Profile %in%  'La France insoumise'] <- 'France_Insoumise'
df$Profile[df$Profile %in%  'partisocialiste'] <- 'Parti_Socialiste'
df$Profile[df$Profile %in%  'lesRepublicains'] <- 'Les_Republicains'
df$Profile[df$Profile %in%  'Europe Écologie-Les Verts'] <- 'Les_Verts'
df$Profile[df$Profile %in%  'placepublique_'] <- 'Place_Publique'
df$Profile[df$Profile %in%  'Reconquete_off'] <- 'Reconquete'
df$Profile[df$Profile %in%  'RNational_off'] <- 'Rassemblement_National'

df$Profile <- ifelse(df$Network == "FACEBOOK", paste0(df$Profile, "_f"),
                     ifelse(df$Network == "TWITTER", paste0(df$Profile, "_t"), df$Profile))

ggplot(df, aes(x = Profile, fill = Network)) + 
  geom_bar() +
  scale_fill_manual(values = c("TWITTER" = "red", "FACEBOOK" = "blue")) +
  labs(title = "Number of posts for each political party",
       x = "Profile", 
       y = "Frequency") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

## Text Preprocessing

```{r}
# Create corpus from df$Message
corpus <- Corpus(VectorSource(df$Message))
corpus
#inspect(corpus)
```

Functions

```{r}
remove_function <-content_transformer(function(x, pattern) gsub(pattern,' ',x))

remove_emoji <- function(text) {
  text <- gsub("[\U{1F600}-\U{1F64F}]", " ", text, perl=TRUE) # Remove Emoticons
  text <- gsub("[\U{1F300}-\U{1F5FF}]", " ", text, perl=TRUE) # Remove symbols and Pictogram
  text <- gsub("[\U{1F680}-\U{1F6FF}]", " ", text, perl=TRUE)# Remove maps   
  text <- gsub("[\U{2600}-\U{26FF}]", " ", text, perl=TRUE) # Remove symbols
  text <- gsub("[\U{2700}-\U{27BF}]", " ", text, perl=TRUE) # Remove Dingbats
  text <- gsub("[\U{1F900}-\U{1F9FF}]", " ", text, perl=TRUE) # Remove emoji Supplemental Symbols and Pictographs
  text <- gsub("⤵️"," ", text, perl=TRUE)
  text <- gsub("▶️"," ", text, perl=TRUE)
  text <- gsub("⬇️"," ", text, perl=TRUE)
  text <- gsub("↩️"," ", text, perl=TRUE)
  text <- gsub("⏰"," ", text, perl=TRUE) 
  text <- gsub("⏱"," ", text, perl=TRUE) 
  text <- gsub("€"," ", text, perl=TRUE) 
  return(text)
}

remove_text_after_emoji <- function(text) {
  text <-gsub("(➡️ )(.*)","\\1", text, perl=TRUE)
  text <- gsub("(⤵️)(.*)","\\1", text, perl=TRUE)
  text <- gsub("(▶️)(.*) ","\\1", text, perl=TRUE)
  text <- gsub("(⬇️)(.*)","\\1", text, perl=TRUE)
  text <- gsub("(↩️)(.*)","\\1", text, perl=TRUE) 
  return(text)
}

remove_urls <- function(text) {
  text <- gsub("(f|ht)tp(s?)://[^ ]+", " ", text) #remove url and links
  text <- gsub("bit\\.ly/\\w+", " ", text)
  return(text)
}

remove_hashtags <- function(text) {
  text <- gsub("#\\w+", " ", text) #remove hashtags and words in the hashtags
  return(text)
}

remove_outside_quotes <- function(text) {
  text <- gsub("^[^\"]*\"|\"[^\"]*$", " ", text) #remove everything outside « »
  return(text)
}

remove_words_after_at <- function(text) {
  text <- gsub("\\s*@\\S+", " ", text) #remove words connected to @
  return(text)
}

remove_spaces<- function(x) {
    gsub("^[[:space:]]*"," ",x) # remove leading whitespaces
    gsub("[[:space:]]*$"," ",x) # remove trailing whitespaces
    gsub(' +', ' ', x) # remove extra whitespaces
}

remove_stopwords <- function(testo) {
  # Lista di articoli, preposizioni e pronomi francesi
  francesi <- c("le", "la", "les", "un", "une", "des", "du", "de", "au", "aux", "à", "avec", "chez", "pour", "par", "dans", "sur", "sous", "en", "vers", "depuis", "pendant", "entre", "jusqu'à", "avec", "sans", "comme", "par", "pour", "selon", "chez", "en", "vers", "entre", "envers", "malgré", "avec", "pour", "contre", "chez", "dans", "par", "pour", "avec", "sans", "sous", "sur", "vers", "avec", "dans", "en", "pour", "chez", "dans", "en", "entre", "par", "sous", "sur", "vers", "après", "avant", "contre", "depuis", "derrière", "devant", "pendant", "pour", "après", "avant", "avec", "contre", "dans", "de", "depuis", "en", "entre", "par", "pendant", "pour", "sans", "sous", "sur", "vers", "versus", "dans", "en", "pour", "par", "parmi", "selon", "sous", "sur", "de", "en", "pour", "de", "par", "pour", "sans", "vers", "dans", "en", "entre", "par", "sous", "sur", "vers", "contre", "par", "pour", "par", "sous", "vers", "contre", "entre", "versus", "dans", "en", "pour", "chez", "par", "sous", "sur", "vers", "dès", "plus", "rt", "non","ça","là","où")
  for (f in francesi) {
    text <- gsub(paste0("\\b", f, "\\b"), " ", testo, ignore.case = TRUE)
  }
  return(text)
}

remove_text_retweet <- function(text) {
  text <-gsub("(rt )(.*)","\\1", text, perl=TRUE)
  return(text)
}

```

Simple syntathic preprocessing: -trasformations in lower letters -remove
special characters -remove puntuaction -remove words with 1 letter
-remove hashtags and urls -remove stopwords -remove spaces

```{r}
suppressWarnings({
  #preprocessing
  corpus <- tm_map(corpus, content_transformer(tolower))
  
  corpus <- tm_map(corpus, remove_function, "\r\n\r\n")
  corpus <- tm_map(corpus, remove_function, "\r\n")
  corpus <- tm_map(corpus, remove_function, "\n")
  
  corpus <- tm_map(corpus, content_transformer(remove_urls))
  corpus <- tm_map(corpus, content_transformer(remove_hashtags))
  corpus <- tm_map(corpus, content_transformer(remove_words_after_at))
  
  corpus <- tm_map(corpus, content_transformer(remove_text_after_emoji))
  corpus <- tm_map(corpus, content_transformer(remove_emoji))
  
  corpus <- tm_map(corpus, removeWords, stopwords('french'))
  corpus <- tm_map(corpus, content_transformer(remove_stopwords))
  corpus <- tm_map(corpus,removeNumbers)
  
  corpus <- tm_map(corpus,remove_function, "\\b\\w{1}\\b") #remove words with 1 letter
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, remove_function, "’")
  corpus <- tm_map(corpus, remove_function, "“")
  corpus <- tm_map(corpus, remove_function, "”")
  corpus <- tm_map(corpus, remove_function, "…")
  corpus <- tm_map(corpus, remove_function, "–")
  corpus <- tm_map(corpus, remove_function, "·")
  
  corpus <- tm_map(corpus, content_transformer(remove_outside_quotes))
  corpus <- tm_map(corpus, remove_function, "«")
  corpus <- tm_map(corpus, remove_function, "»")
  
  corpus <- tm_map(corpus, content_transformer(remove_text_retweet))
  corpus <- tm_map(corpus, remove_function, "rt")

  corpus <- tm_map(corpus, trimws) #remove whitespaces at the beginning and at the end of the paragraph
  corpus <- tm_map(corpus,stripWhitespace)
})

```

Bigrams creation

```{r}
suppressWarnings({
replace_function <- content_transformer(function(x, pattern, replacement) {
  gsub(pattern, replacement, x)
})

corpus <- tm_map(corpus, replace_function, pattern = "manon aubry", replacement = "manon_aubry")
corpus <- tm_map(corpus, replace_function, pattern = "marie toussaint", replacement = "marie_toussaint")
corpus <- tm_map(corpus, replace_function, pattern = "jordan bardella", replacement = "jordan_bardella")
corpus <- tm_map(corpus, replace_function, pattern = "sarah knafo", replacement = "sarah_knafo")
corpus <- tm_map(corpus, replace_function, pattern = "raphaël glucksmann", replacement = "raphaël_glucksmann")
corpus <- tm_map(corpus, replace_function, pattern = "olivier faure", replacement = "olivier_faure")
corpus <- tm_map(corpus, replace_function, pattern = "eric ciotti", replacement = "eric_ciotti")
corpus <- tm_map(corpus, replace_function, pattern = "union populaire", replacement = "union_populaire")

corpus <- tm_map(corpus, replace_function, pattern = "françoisxavier bellamy", replacement = "bellamy")
corpus <- tm_map(corpus, replace_function, pattern = "françois-xavier bellamy", replacement = "bellamy")
corpus <- tm_map(corpus, replace_function, pattern = "françois bellamy", replacement = "bellamy")
corpus <- tm_map(corpus, replace_function, pattern = "éric zemmour", replacement = "zemmour")
corpus <- tm_map(corpus, replace_function, pattern = "marion maréchal", replacement = "maréchal")
corpus <- tm_map(corpus, replace_function, pattern = "marion marechal", replacement = "maréchal")
corpus <- tm_map(corpus, replace_function, pattern = "emmanuel macron", replacement = "macron")

corpus <- tm_map(corpus, replace_function, pattern = "von der leyen", replacement = "von_der_leyen")
corpus <- tm_map(corpus, replace_function, pattern = "françois mitterrand", replacement = "françois_mitterrand")
corpus <- tm_map(corpus, replace_function, pattern = "bastien lachaud panot", replacement = "panot")
corpus <- tm_map(corpus, replace_function, pattern = "bastien panot", replacement = "panot")
})
```

```{r}
#inspect(corpus)
```

-Stemming -Term Document Matrix -Bag of words with term frequency

```{r}
suppressWarnings({
#tdm without stemming
tdm_1 <- DocumentTermMatrix(corpus)
print('Term-document matrix before stemming: ')
print(tdm_1) 

#tf
corpus <- tm_map(corpus, stemDocument, language = 'french')
tdm <- DocumentTermMatrix(corpus)
print('Term-document matrix after stemming: ')
print(tdm)
})

"
#tf-idf
suppressWarnings({
  tdm_1 <- DocumentTermMatrix(corpus, control = list(weighting = function(x) weightTfIdf(x, normalize = FALSE)))
  print(tdm_1)
  
  corpus <- tm_map(corpus, stemDocument, language = 'french')
})
"
```

inspect the term-document matrix

```{r}
tdm_df <- as.data.frame(as.matrix(tdm))
#tdm_df
```

## global words frequency and removing rare words

```{r}
#column frequencies
column_frequencies <- colSums(tdm_df)
frequency_df <- data.frame(t(column_frequencies))
print(frequency_df)

#common words and rare words
frequency_df_transposed <- t(frequency_df)
frequency_tbl <- as_tibble(frequency_df_transposed)

quantile(frequency_tbl$V1, probs = 0.5) 
quantile(frequency_tbl$V1, probs = 0.6) 
quantile(frequency_tbl$V1, probs = 0.7)
quantile(frequency_tbl$V1, probs = 0.8)
quantile(frequency_tbl$V1, probs = 0.9)
quantile(frequency_tbl$V1, probs = 0.95)
quantile(frequency_tbl$V1, probs = 0.96)
quantile(frequency_tbl$V1, probs = 0.97)
quantile(frequency_tbl$V1, probs = 0.98)
quantile(frequency_tbl$V1, probs = 0.99)
quantile(frequency_tbl$V1, probs = 1)

word_freq_under6 <- names(column_frequencies)[column_frequencies < 6]
rare_words_list <- as.list(word_freq_under6 )

tdm_df <- tdm_df[, !colnames(tdm_df) %in% rare_words_list]

column_frequencies <- colSums(tdm_df)
frequency_df <- data.frame(t(column_frequencies))
frequenze <- as.numeric(frequency_df[1, ])
ordered_indices <- order(frequenze, decreasing = TRUE)
ordered_frequency_df <- frequency_df[, ordered_indices]

```

```{r}
final_df <- subset(tdm_df, select = -c(celui,des,mati,sol,ceux,voi,sub,tres,not,tout,beaucoup,autr,comm,poch,une,environ,oui,là,ça,entre,encor,jusqu,icip,apres,toujour,non,moin,dont,depuis,plusieur,mieux,déjà,qua,quoi,pou))

final_df<-final_df[ , -172]
final_df<-final_df[ , -605]
final_df<-final_df[ , -787]
final_df<-final_df[ , -874]
```

## Most popular words

```{r}
term_freq <- colSums(as.matrix(tdm_df))
names(term_freq) <- colnames(tdm_df)
term_freq<- subset(term_freq, term_freq>=20)
df_plot<- data.frame(term = names(term_freq), freq = term_freq)

# Plot word frequency
df_plot<- df_plot %>%
  top_n(30)

ggplot(df_plot, aes(x = reorder(term, +freq), y = freq, fill = freq)) + geom_bar(stat = "identity")+ scale_colour_gradientn(colors = terrain.colors(10))+ xlab("Terms")+ ylab("Count")+coord_flip()

```

## Words cloud

```{r}
suppressWarnings({
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)

matrix <- as.matrix(tdm_df) 
matrix <- t(matrix)
words <- sort(rowSums(matrix),decreasing=TRUE) 
dfw <- data.frame(word = names(words),freq=words)

set.seed(1234) 
wordcloud(words = dfw$word, freq = dfw$freq, min.freq = 1,           
          max.words=1000, random.order=FALSE, rot.per=0.35,            
          colors=brewer.pal(8, "Dark2"))

wordcloud2(data=dfw, size=1.6, color='random-dark', shape='pentagon')
})

```

words for each party\
CREATION OF THE CSV (GO TO FILE words per party.rmd)

```{r}
suppressWarnings({
corpus_content <- sapply(corpus, as.character)

new_df <- data.frame(Corpus = corpus_content, Profile = df$Profile, Network = df$Network, Num_Likes = df$`Number of Likes`, Num_Comments = df$`Number of comments`, Num_Reactions = df$`Number of Reactions, Comments & Shares`, Interaction_Rate = df$`Post interaction rate`)

print(dim(new_df))

library(openxlsx)
excel_file <- "Words.xlsx"
write.xlsx(new_df, excel_file)
})

```

## Sentiment analysis with syuzhet

<https://www.saifmohammad.com/WebPages/NRC-Emotion-Lexicon.htm>
Sentiment analysis, also known as opinion mining, is an umbrella term
for a number of processes for automatically calculating the degree of
negativity or positivity in a text. The dictionary for syuzhet is
available for 108 languages and is able to classify positive and
negative documents. It is able to classify the text in other 8 sentiment
too.

Posts general sentiment

```{r}
suppressWarnings({
library(syuzhet)
library(lubridate)
library(ggplot2)
library(scales)
library(reshape2)
library(dplyr)
})

tweets <- new_df$Corpus

# Ottieni i sentimenti utilizzando get_nrc_sentiment
s <- get_nrc_sentiment(tweets)

# Order bars
#s <- s[, rev(order(colSums(s)))]

# Get sentiments using get_nrc_sentiment
s <- get_nrc_sentiment(tweets)

# Barplot for positive and negative sentiments
positive_negative <- s[, c("positive", "negative")]
barplot(colSums(positive_negative),
        las = 2,
        col = 'blue',
        ylab = 'Count',
        main = 'Positive and Negative Sentiment Scores')

# Specify order for emotions
emotions_order <- c("joy", "trust", "surprise", "fear", "sadness", "disgust", "anger", "anticipation")

# Reorder columns according to specified order
other_sentiments <- s[, emotions_order]

# Create a barplot with angled emotions as labels
barplot(colSums(other_sentiments),
        las = 2,                      # Rotate labels by 90 degrees
        col = 'red',                 # Set bar color to red
        ylab = 'Count',              # Label for y-axis
        main = 'Other Sentiment Scores', # Title of the plot
        cex.names = 0.8,             # Reduce the size of labels
        names.arg = emotions_order,  # Specify names for the x-axis
        cex.axis = 0.8)


```

```{r}
df_sent <- new_df %>%
  mutate(Profile = substr(Profile, 1, nchar(Profile) - 2)) %>%  #Remove last 2 letters
  mutate(orientation = "centre/centre left") %>%
  mutate(orientation = ifelse(Profile %in% c("France_Insoumise"), "left", orientation),
         orientation = ifelse(Profile %in% c("Reconquete", "Rassemblement_National", "Les_Republicains"), "right", orientation))

#add column 'Profile' in s
merged_df <- cbind(Profile = df_sent$Profile, orientation = df_sent$orientation, s)
```

```{r}
# sentiments for each orientation
sentiment_by_orientation <- merged_df %>%
  select(-Profile) %>%
  group_by(orientation) %>%
  summarise_all(sum) %>%
  tidyr::gather(key = "Sentiment", value = "Count", -orientation)

# Divide sentiments and emotions
positive_negative_orientation <- sentiment_by_orientation %>%
  filter(Sentiment %in% c("positive", "negative"))

other_sentiments_orientation <- sentiment_by_orientation %>%
  filter(!Sentiment %in% c("positive", "negative"))

# barplot positive and negative sentiments
ggplot(positive_negative_orientation, aes(x = Sentiment, y = Count)) +
  geom_bar(stat = "identity", fill = 'blue') +
  facet_wrap(~orientation, scales = "free") +
  labs(title = "Positive and Negative Sentiment Scores by Orientation",
       x = "Sentiment",
       y = "Count",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

# estabilish the order
emotions_order <- c("joy", "trust", "surprise", "fear", "sadness", "disgust", "anger", "anticipation")
other_sentiments_orientation$Sentiment <- factor(other_sentiments_orientation$Sentiment, levels = emotions_order)

# Disegna il barplot per gli altri sentimenti
ggplot(other_sentiments_orientation, aes(x = Sentiment, y = Count)) +
  geom_bar(stat = "identity", fill = 'blue') +
  facet_wrap(~orientation, scales = "free") +
  labs(title = "Other Sentiment Scores by Orientation",
       x = "Sentiment",
       y = "Count",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

```

same barplots but in different windows

```{r}
# Filtra i dati per orientamento "left"
left_sentiments <- other_sentiments_orientation %>%
  filter(orientation == "left")

# Disegna il barplot per i sentimenti orientamento "left"
ggplot(left_sentiments, aes(x = Sentiment, y = Count)) +
  geom_bar(stat = "identity", fill = 'blue') +
  labs(title = "Other Sentiment Scores for Left Orientation",
       x = "Sentiment",
       y = "Count",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

# Filtra i dati per orientamento "center"
center_sentiments <- other_sentiments_orientation %>%
  filter(orientation == "centre/centre left")

# Disegna il barplot per i sentimenti orientamento "center"
ggplot(center_sentiments, aes(x = Sentiment, y = Count)) +
  geom_bar(stat = "identity", fill = 'blue') +
  labs(title = "Other Sentiment Scores for Center/Center Left Orientation",
       x = "Sentiment",
       y = "Count",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

# Filtra i dati per orientamento "right"
right_sentiments <- other_sentiments_orientation %>%
  filter(orientation == "right")

# Disegna il barplot per i sentimenti orientamento "right"
ggplot(right_sentiments, aes(x = Sentiment, y = Count)) +
  geom_bar(stat = "identity", fill = 'blue') +
  labs(title = "Other Sentiment Scores for Right Orientation",
       x = "Sentiment",
       y = "Count",
       fill = "Sentiment") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

```

## CA-GALT

In order to have a better plot visualization, it may be useful removing
more rare words Y (prima): a data frame with n rows (individuals) and p
columns (frequencies) X (seconda): a data frame with n rows
(individuals) and k columns (variables)

```{r}
library(FactoMineR)
library(dplyr)

rownames(final_df) <- NULL
final_df 


final_df$Profile = df$Profile

#first df
final_df = final_df %>% 
  as.data.frame() %>%
  mutate(Profile = substr(Profile, 1, nchar(Profile) - 2)) %>%
  group_by(Profile) %>% 
  filter(rowSums(across(where(is.numeric)))!=0) %>%
  summarise(across(everything(), sum)) 
final_df

#first df
prima = final_df %>% select(-Profile)

#second df
seconda = final_df %>%   
  mutate(orientation = "centre") %>%
  mutate(orientation = ifelse(Profile %in% c("France_Insoumise", "Parti_Socialiste", "Place_Publique"), "left", orientation),
         orientation = ifelse(Profile %in% c("Reconquete", "Rassemblement_National", "Les Républicains"), "right", orientation)) %>%
  select(Profile, orientation)

seconda = seconda %>% dplyr::select(Profile,orientation) %>% 
  mutate(Profile = as.factor(Profile), 
         orientation = as.factor(orientation))

cagal = CaGalt(prima, seconda, type = "n")
plot.CaGalt(cagal)
```

```{r}
cagal
cagal$eig

cagal$quali.var$coord %>% ggplot(aes(x = Dim.1, y = Dim.2)) + geom_point() + geom_text(label = rownames(cagal$quali.var$coord))
cagal$quali.var$coord %>% ggplot(aes(x = Dim.1, y = Dim.3)) + geom_point() + geom_text(label = rownames(cagal$quali.var$coord))
cagal$quali.var$coord %>% ggplot(aes(x = Dim.1, y = Dim.4)) + geom_point() + geom_text(label = rownames(cagal$quali.var$coord))


t = cagal$freq$coord %>% as.data.frame()
t$importanza = cagal$freq$contrib %>% rowSums(1:4)
t = t %>% filter(importanza > mean(importanza))
t$l = rownames(t)
```

```{r}
t %>% ggplot(aes(x = Dim.1, y = Dim.2)) + geom_point() + geom_label(label = t$l, hjust = 0, nudge_x = 0.05)

t %>% ggplot(aes(x = Dim.1, y = Dim.3)) + geom_point() + geom_label(label = t$l)

t %>% ggplot(aes(x = Dim.1, y = Dim.4)) + geom_point() + geom_label(label = t$l)
```
